Loop

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

 this stupid figure has to get embedded    
 ![Fig1](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%201..png)

@@

 ![Fig2](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%202.png)

>>>>

 this stupid figure has to get embedded    
 ![Fig1](/Figures/Figure%201.png)

@@

 ![Fig2](./Figures/Figure%202.png)
